\documentclass[a4paper,11pt]{article}

\usepackage{revy}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[danish]{babel}

\revyname{DIKUrevy}
\revyyear{1979}
\version{1.0}
\eta{$n$ minutter}
\status{Færdig}

\title{Sprogforbistring}
\author{APR, OC, KK}
\melody{?: ``I say tomatoes...''}

\begin{document}
\maketitle

\begin{roles}
\role{S1}[A] Sanger 1
\role{S1}[B] Sanger 2
\end{roles}

\begin{props}
\prop{USA-trøje}[]
\prop{Reel til bandet}[Bandet]
\end{props}

\begin{song}
\sings{A} I say array
\sings{B} Hva' gir du et sæt?
 
\sings{A} I say assembler 
\sings{B} og jeg sir symbolsk maskinsprogsoversætter

\sings{A} array
\sings{B} Et sæt!

\sings{A} assembler
\sings{B} symb. mask.s.o.

\sings{A} Let's call the whole thing off.

\sings{A} I say to edit
\sings{B} og jeg sir at redigere

\sings{A} I say to bootstrap
\sings{B} og jeg sir grundsystemgenerere.

\sings{A} edit
\sings{B} redigere

\sings{A} bootstrap
\sings{B} grundsystemgenerere

\sings{B} La' os kalde det hele A 38

\sings{A} Here comes an interlude - a mean time to repair
\sings{B} Hva'

\sings{A} Mean time to repair
\sings{B} Agurketid, sir vi her.

\sings{A} I say a form feed
\sings{B} og jeg siger fodform
\sings{A} I say to back space
\sings{B} og jeg sir tobaksrum
\sings{A} form feed
\sings{B} formfod
\sings{A} to back space
\sings{B} tobaksrum
\sings{A} Then you can smoke and rise.

\sings{A} I say computer
\sings{B} og jeg sir kompuder
\sings{A} I say appendix
\sings{B} og jeg siger blindtarm.
\sings{A} prefix
\sings{B} suffix
\sings{A} appendix
\sings{B} blindtarm
\sings{B} sproget er blevet betændt.

\sings{B} Kender du så den længste term?
\sings{A} Oh, no. Which one?
\sings{B} E4 går fra Leningrad til Lissabon

\sings{A} I say a flow chart
\sings{B} \act{efter en pause} Det bruger vi ikke her!
\sings{A} I say goto
\sings{B} og jeg sir struktureret programmering.
\sings{A} flow chart
\sings{B} \act{tier}
\sings{A} goto
\sings{B} \act{surt} Hell!
\sings{A} Let's call the whole thing off ... for a while.

\sings{B} Jeg siger broktid
\sings{A} and I say machine spoilt work time
\sings{B} Jeg siger dødskøn
\sings{A} and I say post mortem dump.
\sings{B} broktid
\sings{A} m.s.w.t.
\sings{B} død(s)skøn
\sings{A} p.m.d.
\sings{B} det er så trist, så trist \act{tager en spole op}

\sings{A} You can't place you tape on that, it is a Sailors reel
\act{Klaveret spiller en reel}
\sings{B} Post morten dump er blot et ligsyn på en nekro-fil.

\sings{A} I say a line feed
\sings{B} den springer vi over
\sings{A} I say a hand punch
\sings{B} og jeg sir huller med manuel indføring
\sings{A} line feed
\sings{B} \act{begynder} huller med...
\sings{A} hand punch
\sings{B} ...indføring.
\sings{A} Mind the whole hole holds on.

\sings{A} I say monitor
\sings{B} og jeg sir en ordensduks.
\sings{A} I say on line
\sings{B} og jeg sir direkte styring.
\sings{A} monitor
\sings{B} Orden!
\sings{A} on line
\sings{B} Styring!
\sings{A} Let's call the whole thing off-line
\sings{Begge} Let's call the whole thing off.
\end{song}

\end{document}
